\documentclass[12pt,a4paper]{article}

% ================= Packages =================
\usepackage{geometry}
\usepackage{setspace}
\usepackage{longtable}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{array}

% ================= Page Setup =================
\geometry{margin=1in}
\onehalfspacing

\begin{document}

% ================= Title Page =================
\begin{titlepage}
\centering
\vspace*{2cm}

{\LARGE \textbf{Software Requirements Specification}}\\[0.5cm]
{\Large \textbf{Amar Ahmad Khan Academy (AAK Academy)}}\\[1.5cm]

{\large \textbf{ANSI/IEEE Std 830-1984}}\\[2cm]

\textbf{Prepared By}\\[0.8cm]

\begin{tabular}{ll}
\textbf{Name:} & Salman Safdar \\
\textbf{Roll No:} & NUM-BSCS-2024-70 \\[0.5cm]
\textbf{Name:} & Muhammad Haris \\
\textbf{Roll No:} & NUM-BSCS-2024-49 \\[0.5cm]
\textbf{Name:} & Farwa Imran \\
\textbf{Roll No:} & NUM-BSCS-2024-22 \\
\end{tabular}

\vfill

\textbf{Course: Software Engineering}\\
\textbf{Namal University Mianwali}\\
\textbf{Semester Project}\\
\textbf{Date: \today}

\vfill
\end{titlepage}

\tableofcontents
\newpage

% ==================================================
\section{Introduction}

\subsection{Purpose}
This document specifies the functional and non-functional requirements of the Amar Ahmad Khan Academy (AAK Academy) Learning Management System. It serves as a formal reference for development, evaluation, and academic assessment.

\subsection{Scope}
AAK Academy is a web-based LMS that delivers structured online education through fixed-duration courses. The system supports user registration, authentication, monthly payments via bank cards, live and recorded classes, attendance tracking, assignments, quizzes, and GPA-based grading.

\subsection{Definitions and Acronyms}
\begin{itemize}
    \item LMS – Learning Management System
    \item SRS – Software Requirements Specification
    \item JWT – JSON Web Token
    \item GPA – Grade Point Average
\end{itemize}

% ==================================================
\section{Overall Description}

\subsection{Product Perspective}
AAK Academy follows a client-server architecture and integrates external services such as bank card payment gateways and Zoom video conferencing.

\subsection{User Classes}
\begin{itemize}
    \item Students
    \item Faculty
    \item Administrators
\end{itemize}

\subsection{Operating Environment}
\begin{itemize}
    \item Web Browsers (Chrome, Firefox, Edge)
    \item Operating Systems: Windows, macOS, Linux, Android, iOS
\end{itemize}

\subsection{Assumptions}
\begin{itemize}
    \item The system supports up to 1000 concurrent users.
    \item Users have uninterrupted internet access.
\end{itemize}

% ==================================================
\section{Functional Requirements}

\subsection{Authentication and Registration}
\begin{itemize}
    \item FR-001: The system shall allow first-time users to register by providing name, email, and selected course details.
    \item FR-002: The system shall send registration confirmation via email.
    \item FR-003: The system shall allow registered users to log in using email or user ID and password.
    \item FR-004: The system shall authenticate users using JWT-based authentication.
\end{itemize}

\subsection{Course and Enrollment}
\begin{itemize}
    \item FR-005: Courses shall have a fixed duration of six months.
    \item FR-006: Students shall enroll in multiple courses simultaneously.
    \item FR-007: Course access shall be granted only after successful payment.
\end{itemize}

\subsection{Payment Management}
\begin{itemize}
    \item FR-008: The system shall support payments via bank cards (Visa and MasterCard) only.
    \item FR-009: Payments shall be charged on a monthly basis.
    \item FR-010: Payments shall be mandatory before accessing course content.
    \item FR-011: The system shall not support any refund mechanism.
\end{itemize}

\subsection{Live Classes and Attendance}
\begin{itemize}
    \item FR-012: The system shall conduct live classes using Zoom.
    \item FR-013: Live classes shall be mandatory with attendance marking.
    \item FR-014: Recorded sessions shall be stored in the LMS.
    \item FR-015: Students missing live classes may view recordings but shall lose attendance marks.
\end{itemize}

\subsection{Assignments and Quizzes}
\begin{itemize}
    \item FR-016: Students shall submit assignments online within defined deadlines.
    \item FR-017: Students may resubmit assignments within the allowed time.
    \item FR-018: Quizzes shall allow only a single attempt.
    \item FR-019: Quizzes shall be available only within a specific time window.
\end{itemize}

\subsection{Grading}
\begin{itemize}
    \item FR-020: Faculty shall manually evaluate assignments and quizzes.
    \item FR-021: Student performance shall be calculated using GPA grading.
\end{itemize}

\subsection{Notifications}
\begin{itemize}
    \item FR-022: The system shall send email notifications for registration, payments, quizzes, and deadlines.
\end{itemize}

\subsection{Administration}
\begin{itemize}
    \item FR-023: Administrators shall manage users, courses, and grades.
    \item FR-024: Administrators shall disable user accounts when required.
    \item FR-025: Administrators shall not modify payment records.
\end{itemize}

% ==================================================
\section{Non-Functional Requirements}

\subsection{Performance}
\begin{itemize}
    \item NFR-001: The system shall support at least 1000 concurrent users.
\end{itemize}

\subsection{Security}
\begin{itemize}
    \item NFR-002: All transactions shall be processed over HTTPS.
    \item NFR-003: Payment data shall comply with card security standards.
\end{itemize}

\subsection{Reliability}
\begin{itemize}
    \item NFR-004: System uptime shall be at least 99.5\%.
\end{itemize}

% ==================================================
\section{External Interfaces}

\subsection{Software Interfaces}
\begin{itemize}
    \item Bank Card Payment Gateway (Visa/MasterCard)
    \item Zoom API
    \item MongoDB Database
\end{itemize}

% ==================================================
\section{Future Enhancements}
\begin{itemize}
    \item Mobile application development
    \item AI-based student analytics
\end{itemize}

\end{document}
